Statically Typed String Sanitation Inside a Python

### 2014-08-19 sanitation-psp14/sanitation-psp14-short.tex
Added defsheet.

In this section, we define $\lambdas$, describe each operation, and finally prove both type safety and a correctness result for the language.
The grammar for $\lambdas$ is defined in Figure \ref{fig:glambdas}. Typing rules \textsc{S-T-} are defined in Figure \ref{fig:slambdas} and a big-step semantics
is defined in Figure \ref{fig:dlambdas}
\footnote{For the reader's convienance, a single sheet containing figures \ref{fig:glambdas}-\ref{fig:tr} is available at http://nfulton.org/strings/printout.pdf \todo{post this}}.

>>>>

In this section, we define $\lambdas$, describe each operation, and finally prove both type safety and a correctness result for the language.
The grammar for $\lambdas$ is defined in Figure \ref{fig:glambdas}. Typing rules \textsc{S-T-} are defined in Figure \ref{fig:slambdas} and a big-step semantics
is defined in Figure \ref{fig:dlambdas}
\footnote{For the reader's convienance, a single sheet containing figures \ref{fig:glambdas}-\ref{fig:tr} is available at http://nfulton.org/strings/printout.pdf.}.
